---
title: "Integration of AI and R Programming"
author: "Dadong Zhang"
format:
  pdf:
    include-in-header:
      text: |
        \usepackage{fvextra}
        \fvset{breaklines=true,breakanywhere=true}
editor: visual
---

## Demonstration of inplementing OpenAI in R programming for generating neat document in PDF, Presentation, and Word.


```{r global-setup, echo=TRUE}
rm(list = ls())
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(httr)
library(jsonlite)
library(flextable)
library(table1)
set.seed(123)
options(width = 70)
source("src/func.R")
```

## Ask AI to generate a dummey patient characteristic, demogrphaic, baseline, treatment, and binary clinical response data set

```{r echo=TRUE}
question <- "Can you give R code to generate a dummy data frame for 100 patients with their characteristics such as gender, age, bmi, height, race, baseline, treatment, and binary clinical response data set?"
result1 <- chatgpt_query_with_history(question)
cat("Assistant's answer:\n", result1$answer, "\n")

# Optionally, extract R code:
eval(parse(text = extract_r_code(result1)))
```
## Continue asking AI to make a characteristics table for the patients betweo treatment

```{r echo=TRUE}
question2 <- "Can you give me the R code to generate the patient characteristics
table using R package table1 between treatment? I already installed the package."
result2 <- chatgpt_query_with_history(question2, history = result1$history)
cat("Assistant's answer:\n", result2$answer, "\n")
eval(parse(text = extract_r_code(result2)))
```
## Continue asking AI to make a bar plot for the response rate between the treatment groups

```{r echo=TRUE}
question3 <- "Can you give me the R code to make a barplot for the response 
rates between treatment groups?"
result3 <- chatgpt_query_with_history(question3, history = result1$history)
cat("Assistant's answer:\n", result3$answer, "\n")
eval(parse(text = extract_r_code(result3)))
```

## Continue asking AI to statistical test for the response rate between the treatment groups

```{r}
question4 <- "Can you give me the R code to evaluate statistical differences for
the response rates between treatment groups?"
result4 <- chatgpt_query_with_history(question4, history = result1$history)
cat("Assistant's answer:\n", result4$answer, "\n")
eval(parse(text = extract_r_code(result4)))
```